\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 
\namesection{Jerry}{Zhou}{ 
}
\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 
\namesectionright{ 
2B Honours Computer Science Co-op \\
\urlstyle{same}\url{http://jerryzhou.net} | \href{mailto:contact@jerryzhou.net}{contact@jerryzhou.net} | 647.926.5096
}
\end{minipage} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Languages}
\location{Proficient:}
Javascript \textbullet{} CSS \\
Python \textbullet{} Swift \\
\location{Familiar:}
C++ \textbullet{} Ruby \\
PHP \textbullet{} C\# \textbullet{} Java
\\[5pt]
\subsection{Tools}
Git \textbullet{} Postgres \textbullet{} MySQL \\
Webpack \textbullet{} Unix \textbullet{} AWS \\ 
\\[5pt]
\subsection{Frameworks}
\location{Intimately Familiar:}
ReactJS \textbullet{} AngularJS \textbullet{} Cordova \\
Express \textbullet{} Django \\
\location{Experienced:}
Laravel \textbullet{} Rails \textbullet{} SocketIO \textbullet{} AngularJS2 \\
\sectionsep
\\[5pt]
\subsection{Highly Motivated}
- Audacious, industrious and consistent about goals.\\
- Passionate about ReactJS and frontend web, keeps up with latest developments, is early adopter of many important libraries.\\
- Active FOSS contributor - Published 5+ javascript libraries and frequently participate in open source discussions
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Waterloo}
\descript{Candidate for Bachelor of Computer Science / Software Engineering Option}
\location{Sept 2014 - Present}
\sectionsep

\subsection{Coursera}
\descript{Machine Learning Course}
\location{Jan 2016 - April 2016}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\subsection{Undergraduate}
%Information Retrieval \\
%Operating Systems \\
%Artificial Intelligence + Practicum \\
%Functional Programming \\
%Computer Graphics + Practicum \\
%{\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst) }}} \\
%Unix Tools and Scripting \\
%\sectionsep
\\[48pt]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github: \href{https://github.com/looklikeapro}{\custombold{github.com/looklikeapro}} \\
Website: \href{}{\custombold{jerryzhou.net}} \\
Email: \href{}{\custombold{contact@jerryzhou.net}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{WeMesh}
\descript{| iOS Developer }
\location{Jan 2016 – Apr 2016 | Kitchener, ON}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Developed new WeMesh UI for browsing videos and channels.
\item Refactored and improved video synchronization on client side.
\item Worked efficiently under tight schedules with daily builds and continuous testing.
\item Communicated continuously with team members to keep code interface clean and achieve reuse across application.
\end{tightemize}
\sectionsep

\runsubsection{Nascent Digital Experiences}
\descript{| App Engineer }
\location{May 2015 – Aug 2015 | Toronto, ON}
\begin{tightemize}
\item Developed frontend of <30 Days app with AngularJS and Ionic.
\item Maintained and bug-fixed mature web apps in production.
\item Worked with and improved company application scaffolding with RequireJS, Browserify, Gulp, Grunt.
\item Worked with client, management, team and QA to run effective development process.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Solanum.io}
\descript{| Ongoing}
\begin{tightemize}
\item Built website for discovery and shopping at local farms and farmer's markets.
\item Used ReactJS and Django Rest Framework to create a responsive experience.
\item Organized development effort over many months with planning, CI, unit testing, analytics, backup, etc.
\item Published parts of software as open source libraries. (Python Package Manager, HoverTiles, FarmScraper, TurboWebsite)
\end{tightemize}
\sectionsep

\runsubsection{Student CarShare Mobile App}
\descript{| April 2015}
\begin{tightemize}
\item Developed car rental app for a Canada-wide high profile company.\item Leveraged AngularJS web framework deliver production-ready solution in
short development time.\item Built application scaffold with consideration for security, modularity, extensibility.
\end{tightemize}
\sectionsep

\runsubsection{Unsight Labs Utiliy App Suite}
\descript{| Jan 2014}
\begin{tightemize}
\item Developed and published a number of small iOS utility applications.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Activities} 
\begin{tabular}{lll}
Web App Developer, Renison University College Library & Jan 2015 - Present \\
Hackathon Enthusiast & Sept 2014 - Present\\
Executive, University of Waterloo AppDEV Club & Sept 2014 - Dec 2015\\
Captain, Bayview Secondary School Robotics Team & Sept 2013 - June 2014\\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Interests} 

\begin{tabular}{rll}
Robotics, design, refactoring code, racquet sports, reading \\
\end{tabular}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
